Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-06-08 Master Thesis/synopsis.tex
Abuse of notation notice
Fix Lemma 3.1

$K_v$ is called a \textit{henselization} of $K$ with respect to $v$. Furthermore, $\overline{v}$ has the same value group as $v$ and the same residue field $k(\overline{v}) = k(v)$. $G_{K_v}$ is the decomposition group of the unique extension of $\overline{v}$ to $K^\text{s}$:
\[ G_{\overline{v}} = \{ \sigma\in G_K\mid \sigma(\mathcal{O}_{\overline{v}}) =\mathcal{O}_{\overline{v}} \} \subset G_K \]
Conversely, taking the fixed field of the decomposition group of an extension $\overline{v}'$ of $v$ in $K^\text{s}$ yields a henselization of $K$ with respect to $v$. Any two of such henselizations are $K$-conjugate.
\end{theorem}

@@

By Lemma \ref{2.5}, $E_0/E$, and also $E'_0/E'$, satisfy the condition of Proposition \ref{2.6} for both $\ell_1$ and $\ell_2$. Thus there exists a unique henselian valuation $w'_{E'}\in|\operatorname{Spv}(E')|$. Choose a prime $\ell\neq \operatorname{char} k(w'_{E'})$ from $\ell_1,\ell_2$. Since $\mathrm{H}^3(E',\mathbb{Z}/\ell\mathbb{Z})\cong \mathrm{H}^3(E,\mathbb{Z}/\ell\mathbb{Z})\neq 0$, we get from Lemma \ref{2.5}:
\[\operatorname{rrank}(w'_{E'}) = \dim_{\mathbb{Q}}(\Gamma_{w'_{E'}}\otimes_\mathbb{Z}\mathbb{Q}) \geq \dim_{\mathbb{F}_\ell}(\Gamma_{w'_{E'}}/\ell\Gamma_{w'_{E'}})=2=\dim(E')\]
which makes $w'_{E'}\in\operatorname{Spv}^{(2)}_\text{d}(E')$. Now $E'$ contains a henselization $K'_{w'}$ of $w' = w'_{E'}|_{K'}\in\operatorname{Spv}^{(2)}_\text{d}(K')$. By applying the same argument to $\sigma^{-1}$ we find that $E' = K'_{w'}$.

>>>>

$K_v$ is called a \textit{henselization} of $K$ with respect to $v$. Furthermore, $\overline{v}$ has the same value group as $v$ and the same residue field $k(\overline{v}) = k(v)$. By abuse of notation, we will also write $v$ for $\overline{v}$. $G_{K_v}$ is the decomposition group of the unique extension of $\overline{v}$ to $K^\text{s}$:
\[ G_{\overline{v}} = \{ \sigma\in G_K\mid \sigma(\mathcal{O}_{\overline{v}}) =\mathcal{O}_{\overline{v}} \} \subset G_K \]
Conversely, taking the fixed field of the decomposition group of an extension $\overline{v}'$ of $v$ in $K^\text{s}$ yields a henselization of $K$ with respect to $v$. Any two of such henselizations are $K$-conjugate.
\end{theorem}

@@

By Lemma \ref{2.5}, $E_0/E$, and also $E'_0/E'$, satisfy the condition of Proposition \ref{2.6} for both $\ell_1$ and $\ell_2$. Thus there exists a unique henselian valuation $w'_{E'}\in|\operatorname{Spv}(E')|$. Now $E'$ contains a henselization $K'_{w'}$ with respect to $w' = w'_{E'}|_{K'}$. By applying the same argument to $\sigma^{-1}$ we find that $E' = K'_{w'}$.

It remains to see that $\operatorname{rrank}(w')=2$. Choose a prime $\ell\neq \operatorname{char} k(w')$ from $\ell_1,\ell_2$. Since $\mathrm{H}^3(E'_0(\mu_{\ell}),\mathbb{Z}/\ell\mathbb{Z})\neq 0$ by Lemma \ref{2.6}, we get from Lemma \ref{2.5}:
\[\operatorname{rrank}(w')= \operatorname{rrank}( \widetilde{w}') = \dim_{\mathbb{Q}}(\Gamma_{\widetilde{w}'}\otimes_\mathbb{Z}\mathbb{Q}) \geq \dim_{\mathbb{F}_\ell}(\Gamma_{\widetilde{w}'}/\ell\Gamma_{\widetilde{w}'})=2\]
where $\widetilde{w}'$ is the extension of $w'_{E'}$ to $E'_0(\mu_{\ell})$. This makes $w'\in\operatorname{Spv}^{(2)}_\text{d}(K')$.
